---
title: "Your A4 Report Title (TODO: Revise title)"
author: "Shruti Anand"
date: '2022-11-01'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 

While preparing for this project and doing some background research on incarceration especially in the US
and its effects, I learned a lot. In particular, I learned a lot about how incarceration deeply affects families
and creates a cycle of negative consequences rather than creating a positive change in society and families
of those who are incarcerated. Some particular effects I had read about is how increasing jail populations is not
only becoming a moral concern, but that of a health concern. As populations drastically increase and the main issue
that incarceration attempted to solve is not going away anytime soon, the health of those who are held in jails
is continually deteriorating which is very worrying especially now. 

In terms of stakeholders, I felt that the people who are incarcerated and placed in jails, and the families
of those incarcerated would be the primary stakeholders. They are most affected by drastically increasing incarceration rates and the many issues that are continuing to arise with the increase of incarceration rates
nationwide. 

For this project I planned on focusing on the increase or decrease in the total populations of people
that go to jail yearly and from that broad idea, I planned on narrowing it to states in the Pacific 
Northwest, namely California, Washington, and Oregon to name a few. 


# Test (TODO: Remove before submission!!)
```{r echo=FALSE}
q1_string <- test_query1()
num <- 5
```
As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!** 
* Here's another test. A vector
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction 
[TODO]

## Data Summary 
[TODO]

```{r}
head(incarceration_df)
```

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

